% ============================================
%  Academic CV for PhD Application
%  Jiaqi Zhou — Corpus-Assisted CDA / Computational Discourse Analysis
%  Compiler: XeLaTeX (Overleaf: Menu → Compiler → XeLaTeX)
% ============================================

\documentclass[10pt,a4paper]{article}

% ---------- Page Layout ----------
\usepackage[margin=1.6cm, bottom=1.2cm, top=1.2cm]{geometry}
\usepackage{setspace}
\setstretch{1.05}

% ---------- Fonts ----------
\usepackage{fontspec}
\IfFontExistsTF{Times New Roman}
  {\setmainfont{Times New Roman}}
  {\setmainfont{TeX Gyre Termes}}

% ---------- Colors ----------
\usepackage[dvipsnames]{xcolor}
\definecolor{accent}{HTML}{000000}
\definecolor{dark}{HTML}{333333}
\definecolor{gray}{HTML}{666666}

% ---------- Packages ----------
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{tabularx}
\usepackage[hidelinks, colorlinks=false, urlcolor=black, linkcolor=black, citecolor=black]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome5}

% ---------- No Indent ----------
\setlength{\parindent}{0pt}
\setlength{\parskip}{0.15em}

% ---------- Header/Footer ----------
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\fancyfoot[C]{\footnotesize \thepage}

% ---------- Compact Lists ----------
\setlist{nosep, leftmargin=1.2em, itemsep=0.05em, topsep=0.1em}

% ---------- Section Style ----------
\titleformat{\section}
  {\bfseries\Large\color{accent}}
  {}
  {0pt}
  {}
  [\vspace{-0.4em}\rule{\textwidth}{0.5pt}\vspace{-0.1em}]

\titlespacing{\section}{0pt}{0.6em}{0.15em}

% ---------- Custom Commands ----------
\newcommand{\cventry}[4]{
  \textbf{#1} \hfill \textit{\footnotesize #2} \\
  \footnotesize #3 \\
  \footnotesize #4
  \vspace{0.15em}
}

\newcommand{\pubentry}[1]{
  \footnotesize #1
}

% ---------- Document ----------
\begin{document}

% ==================== HEADER ====================
\begin{center}
  {\Large\bfseries Jiaqi Zhou} \\[0.15em]

  \footnotesize
  \faEnvelope\ \href{mailto:jiaqi_zhou@mails.ccnu.edu.cn}{jiaqi\_zhou@mails.ccnu.edu.cn} \quad
  \faPhone\ (+86) 183-2726-0989 \quad
  \faGlobe\ \href{https://your-site.com}{your-site.com} \\[0.05em]
  \faMapMarker*\ Wuhan, China
\end{center}

\vspace{-0.3em}

% ==================== RESEARCH INTERESTS ====================
\section{Research Interests}

\begin{itemize}
  \item Corpus-Assisted Critical Discourse Analysis
  \item Computational Discourse Analysis \quad\textbullet\quad Critical Discourse Analysis
  \item Computational Linguistics \quad\textbullet\quad AI Ethics \& Media Discourse
\end{itemize}

% ==================== EDUCATION ====================
\section{Education}

\cventry{Central China Normal University -- MA in Linguistics}{Sep 2024 -- Jun 2027}
  {Core Modules: Corpus Linguistics (92.4), Functional Linguistics (90.0), Research Methods in Linguistics (96.0), Applied Linguistics (95.8)}
  {GPA: 4.04/5.0 \quad Weighted Average: 90.6/100}

\cventry{Wuhan University of Science and Technology -- BA in English Language}{Sep 2020 -- Jun 2024}
  {Core Modules: English Linguistics, Advanced English, Research Methods in English, Academic Writing}
  {GPA: 3.58/4.0 \quad Weighted Average: 89.5/100 \quad Outstanding Graduate}

% ==================== RESEARCH EXPERIENCE ====================
\section{Research Experience}

\cventry{Principal Investigator -- Provincial Innovation \& Entrepreneurship Program}{May 2023 -- Jun 2024}
  {Project: ``A Socio-Cultural Investigation of Chinese EFL Learners' Emotional Experiences, Learner Identities, and Identity Transformation'' (Provincial-Level, Supervisor: Associate Prof.\ Zaibo Long)}
  {Led a provincial research project examining emotional experiences and learner identity. Designed longitudinal data collection using stimulated recall and semi-structured interviews.}

\cventry{Research Project -- Independent Research}{Jan 2023 -- Jan 2024}
  {``Visualizing the Knowledge Domain of Sociocultural Theory in SLA: A Bibliometric Analysis'' -- collected Web of Science bibliometric data, constructed co-citation and trend visualizations using CiteSpace}
  {}

% ==================== PUBLICATIONS ====================
\section{Publications}

\subsection*{\normalsize Journal Articles}

\pubentry{
  \textbf{Zhou, J.}, \& Zhang, X. (2026). Language assemblage: By Alastair Pennycook. Cambridge University Press, 2024. \textit{[Journal Name]}. \hfill \textsc{ssci}
}

\pubentry{
  Wang, J., \& \textbf{Zhou, J.} (under review). Revisiting posthumanism in language studies: Twenty years on (2006--2025). \textit{Language Sciences}. \hfill \textsc{ssci}
}

\pubentry{
  Wang, J., \& \textbf{Zhou, J.} (under review). Powerless, passive, and paralyzed individuals facing the surging tide of AI technology. \textit{Language Sciences}. \hfill \textsc{ssci}
}

\pubentry{
  Wang, J., \& \textbf{Zhou, J.} (under review). The passive, muted, and powerless public in the controversial AI revolution. \textit{IEEE Transactions on Professional Communication}. \hfill \textsc{ssci}
}

\pubentry{
  \textbf{Zhou, J.} (under review). Agenda bundling and temporal drift: A multi-method sentiment analysis of AI coverage across mainstream and specialist news media. \textit{Digital Scholarship in the Humanities}. \hfill \textsc{ssci}
}

\pubentry{
  \textbf{Zhou, J.} (under review). Divergent paths of AI ethics governance: A structural topic modeling analysis of Chinese and U.S. policy discourse. \textit{Government Information Quarterly}. \hfill \textsc{ssci}
}

\pubentry{
  \textbf{Zhou, J.}, \& Long, Z. (2024). A bibliometric analysis of international second language identity research (2004--2023). \textit{Advances in Psychology}, 14(7), 472--487. \href{https://doi.org/10.12677/ap.2024.147504}{doi:10.12677/ap.2024.147504}
}

\subsection*{\normalsize Conference Presentations}

\pubentry{
  \textbf{Zhou, J.} (2026, June). \textit{Divergent paths of AI ethics governance.} Digital Intelligence, Language, and the Future Forum, HUST, Wuhan.
}

\pubentry{
  \textbf{Zhou, J.} (2026, May). \textit{Constructing the ``China AI Threat.''} Symposium on Language Governance in the Digital Intelligence Era, Wuhan University, Wuhan.
}

% ==================== TEACHING EXPERIENCE ====================
\section{Teaching Experience}

\cventry{Teaching Assistant -- Central China Normal University}{Sep 2025 -- Jan 2026}
  {Assisted in course preparation and materials development; administered grading and maintained academic records; provided instructional support across weekly sessions.}
  {}

% ==================== HONOURS \& AWARDS ====================
\section{Honours \& Awards}

\begin{itemize}
  \item Graduate Scholarship, Central China Normal University \hfill 2023--2025
  \item Outstanding Graduate, Wuhan University of Science and Technology \hfill 2024
  \item National First Prize, National English Competition (NECCS) \hfill 2023
  \item National First Prize, ``FLTRP\textperiodcentered Wordmaster'' National Vocabulary Competition \hfill 2023
  \item National Third Prize, ``FLTRP\textperiodcentered ETIC'' International Communication Competition \hfill 2025
  \item Third Prize (Written Translation Final), CATTI Cup National Translation Competition \hfill 2023
  \item National Second Prize, National College English Translation Competition \hfill 2022
  \item Third-Class Scholarship, Wuhan University of Science and Technology \hfill 2022
\end{itemize}

% ==================== SKILLS ====================
\section{Skills}

\begin{itemize}
  \item \textbf{Languages:} Mandarin (native), English (IELTS 7.5), Japanese (basic), Cantonese (basic)
  \item \textbf{Methods:} Corpus construction \& annotation, (critical) discourse analysis, computational text analysis (Python, R), statistical modeling, qualitative coding
  \item \textbf{Software:} R, AntConc, WordSmith 9, LancsBox X, UAM CorpusTool, CiteSpace, Python
\end{itemize}

% ==================== ACADEMIC SERVICE ====================
\section{Academic Service}

\begin{itemize}
  \item Organising Committee, The 2nd Interdisciplinary Forum on Language and Cognitive Science, CCNU \hfill 2024
\end{itemize}

% ==================== REFEREES ====================
\section{Referees}

\begin{tabularx}{\textwidth}{XX}
  \textbf{Prof.\ Jiayu Wang} & \textbf{Prof.\ Zaibo Long} \\
  Professor & Associate Professor \\
  Dept.\ of Linguistics, & Dept.\ of Chinese, \\
  Shanghai International Studies University & Wuhan University of Science and Technology \\
  \href{mailto:xxx@xxx.edu.cn}{xxx@xxx.edu.cn} & \href{mailto:xxx@xxx.edu.cn}{xxx@xxx.edu.cn} \\
\end{tabularx}

\vspace{0.3em}

\rule{\textwidth}{0.5pt}
\vspace{0.1em}
\begin{center}
  \footnotesize
  Last updated: June 2026
\end{center}

\end{document}
